Dependent Object Types

### 2012-08-29 doc/candidacy/report.tex
intro to ml paper

>>>>

\subsection{A Type-Theoretic Approach to Higher-Order Modules with Sharing}

In~\cite{homl}, Harper and Lillibridge present a calculus for
first-class modules, with complete control over the propagation of
compile-time information.

Their module system is inspired by Standard ML (SML). The SML module
system has three constructs: {\it signatures}, {\it structures}, and
{\it functors}. A {\it structure} is a module: it defines a collection
of types, values and (sub)structures packaged as a program unit. A
{\it signature} is an interface, the ``type'' of a structure: it
describes the types, values and (sub)structures of a structure by
giving their kinds, types and interfaces. A {\it functor} is a
function mapping structures to structures. SML has a notion of ``type
sharing'' which allows stating that types specified in separate
modules are actually equal.

Their module system addresses some shortcomings of the SML module
system. Though the SML module system is higher-order, because SML
provides functors and substructures, it still treats modules as
second-class. For example, it isn't possible to return a structure
from an if statement. In fact, allowing this might require obscuring
the visibility of the resulting structure to ensure soundness. Another
limitation of the SML module system is that ``type sharing'' is
limited to equality between type names, not general type
expressions. In effect, this means that the transparency / opaqueness
of a signature cannot be fully fine-tuned. Their proposal introduces
translucent signatures, which allows any type to be partially
determined by a type expression.

%Scala's abstract types have close
%resemblances to abstract types of signatures in the module systems of
%ML.

\subsection{A Nominal Theory of Objects with Dependent Types~\cite{nuObj}}

\subsection{Tribe: a simple virtual class calculus~\cite{tribe}}
